---
title: "TSF-GRIP(Feb`23) Supervised-ML using R"
author: "Bhanuprakash"
date: "03/02/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

## Loading dataset of Scores & Hours.
```{r}
df=read.csv("C:\\Users\\Bhanu\\OneDrive\\Desktop\\Tasks\\StudentScores.csv",header = T);df
attach(df)
```

## Summary of the data
```{r}
summary(df)
```

## Plotting the data of Hours v/s Scores
```{r}

scatter.smooth(Hours,Scores,xlab='Hours',ylab='Scores',main='Hours vs. Scores')

```

#### Interpretation: Scores are linearly increasing with hours of study too.


## Identifying Outliers
```{r}
boxplot(df,main='Boxplot')

```

#### Interpretation: No outliers and most of the data lies on upper part.(i.e..right skewed)


## Preparing training and testing sets for modelling

```{r}
library(caret)
set.seed(600)
train_index=createDataPartition(df$Scores,p=0.7,list = F)
trainset=df[train_index,]
testset=df[-train_index,]
print("----Trained----")
```



## Model Building...

```{r}
model=lm(Scores~Hours,data = trainset)
summary(model)
```

## Coefficient of determination(R.Sq)
```{r}
summary(model)$r.squared*100

```

#### 95.2565 % of the variation in the exam scores can be explained by the number of hours studied .



## Predicting Scores based on Model
```{r}
fit.model=fitted(model) ; fit.model

```

## Model Diagnostic Plots

```{r}
# Plot for Predicted v/s Actual Scores
plot(x=predict(model), y= trainset$Scores,
     xlab='Predicted Values',
     ylab='Actual Values',
     main='Predicted vs. Actual Values')
abline(a=0, b=1)


```


```{r}
plot(lm(Scores~Hours,data = trainset))
```

## Plot for cook’s distance
```{r}
cooks.distance(lm(Scores~Hours,data = trainset))

```

```{r}
plot(cooks.distance(lm(Scores~Hours,data = trainset)))
```


## creating function for predicting score
```{r}
Score=function(hrs){
  score=model[[1]][1]+(model[[1]][2])*hrs
  if (hrs >= 2){
      cat("The score is",score,"for studying",hrs,"hours.","\n")
    }
  else{
    cat("The score is",score,"for studying",hrs,"hour.","\n")
    }
}
```

## Testing function()
```{r}
Score(1)
```

```{r}
Score(9.25)
```



## Evaluating Model Accuracy
```{r}
#Root Mean Square Error
#predicted values,testdata

rmse=function(prevar,testdt) sqrt(mean(((testdt - prevar)^2)))

a=rmse(fit.model,testset$Scores)
cat("The performance of the model value is about ",a)

```


# -------Thank You-------






