---
title: "TSF-GRIP(Feb`23) Unsupervised ML using R"
author: "Bhanuprakash"
date: "13/02/2023"
output:
  word_document: default
  html_document: default
---


## Loading required libraries
```{r}
library(factoextra)

```


## Lets prepare the dataset
```{r}
#loading iris data
df1=iris
head(df1)
tail(df1)
```

## Dimension of the data
```{r}
dim(df1)
```


## Summary
```{r}
summary(df1)
```


## Scaling variables for cluster analysis
```{r}
scale.df1=scale(df1[1:4])
head(scale.df1)

```


## Finding Optimal number of clusters for kmeans using plots.
```{r}
# Using method of total within sum of squares
#an Elbow plot
fviz_nbclust(scale.df1, kmeans, method = "wss")

```
###In this method,the cluster point at 3 had some bent position declining continously. therefore optimal no.of clusters is k=3 a/c to this plot.Lets see another method..


```{r}
# Using method of silhouette
fviz_nbclust(scale.df1, kmeans, method = "silhouette")

```
###In this method also cluster point 3 had some bent position. therefore optimal no.of clusters is k=3 .Lets see another method..

```{r}
# Using method of gap_stat
fviz_nbclust(scale.df1, kmeans, method = "gap_stat")

```

###we can see that gap statistic is highest at k = 3 clusters, which matches the wss method.i.e..Elbow method. Lets see what will happen for 50 obs`..


```{r}
# Using method of gap_stat for 50 obs`
fviz_nbclust(scale.df1, kmeans, method = "gap_stat", nboot = 50)

```

###It is same as above...

### From all these plots we can interprest that,the optimal number of clusters occurs at the k = 3.Hence ,our data has 3 cluster formations.


## Computing K-means clustring for k=3 clusters
```{r}
set.seed(246)

k.means = kmeans(scale.df1, centers = 3, nstart = 30)
k.means
```
### It can be identifed that 53,50,47 percent of species are assigned to first,second,third clusters respectively.


## Lets find the means or centroids of each cluster
```{r}
aggregate(scale.df1, by=list(cluster=k.means$cluster), mean)
```
### These are all the centroids of all species dimensions for each cluster.  


## k-means model visualization 
```{r}

fviz_cluster(k.means, data = scale.df1)

```

## Finally, With respect to the problem statement ,it is concluded that there are 3 clusters ( k=3 ) for this iris dataset and visualized it graphically.




# ------ THANK YOU ------







