---
title: "TSF-GRIP(Feb`23) Supervised-ML using R"
author: "Bhanuprakash"
date: "08/02/2023"
output:
  html_document:
    df_print: paged
---

```{r}
#loading iris data
df=iris
head(df)
tail(df)
```

## Summary
```{r}
summary(df)
```


```{r}
#loading required libraries
library(caret)
library(rpart)
library(rpart.plot)

```


## Training the dataset
```{r}
#Create training and testing datasets
set.seed(500)

training_index=createDataPartition(df$Species,p=0.7,list=F)
trainset=df[training_index,]
testset=df[-training_index,]

print("------ Train Completed ------")
```

## Decision Tree Model computing..

```{r}
#defining decision treee model
deci.tree=rpart(Species~.,data=trainset,parms = list(split="gini"))
deci.tree
```

## Plotting Model

```{r}
#plotting decision tree model
rpart.plot(deci.tree,extra = 109)

```

## Making Predictions

```{r}
# predicton with tree model on train data set.

predict.train <- predict(deci.tree,newdata=trainset,type="class")
addmargins(table(predict.train,trainset$Species))

```

```{r}
# predictons with tree model on test data set.

predict.test <- predict(deci.tree,newdata=testset,type="class")
addmargins(table(predict.test,testset$Species))

```

## Accuracy of the Model...
```{r}

#confusion matrix for train set
confusionMatrix(predict.train,trainset$Species)


```
#### Interpretation: Accuracy on the trainset data equals 0.9619,which is 
96.19% .

```{r}
#confusion matrix for test set
confusionMatrix(predict.test,testset$Species)

```
#### Interpretation: Accuracy on the testset data equals 0.9333,which is 
93.33% .

#### Finally ,The decision tree model performs well.Even though the accuracy of the testset is lower than the train set accuracy .


# -------Thank You-------
